### 2022-03-23 ch1.tex
merge in paper 1 critiques and comments
Final committee edits

\hypertarget{intro}{%
\chapter{Introduction}\label{intro}}

% TODO entire dissertation Covid vs COVID vs Coronavirus

This dissertation focuses on how people search for information and how people
rely on this information to inform their health-behaviors and develop social
norms. Information permeates every facet of human society, from the hordes of
data gathered through digital-trace data or the passing gossip between friends.
Human communication and human society are based on the circulation of
information and knowledge. Information can be shared and promoted by others
through information campaigns and consumed by an individual, called information
push, or information can be intentionally sought out by individuals, 
called information pull \citep{cybenkoFoundationsInformationPush1999}.

@@

The importance of reputable information and misinformation was clear
in the recent and ongoing COVID-19 pandemic. While the vaccines against the
COVID-19 virus prevent severe illness, hospitalization, and death, only 60\% of
Arizonans over 12 years old are fully vaccinated against the virus. We know that
people exposed to misinformation are much less likely to receive vaccinations
against the virus \citep{loombaMeasuringImpactCOVID192021}. It is not an
exaggeration to claim that misinformation has been deadly for Arizona
\citep{pathakInfodemicsCOVID19Role2020, greene_murphy21}.

This dissertation on information search and norm development provides clear and
timely social implications for Arizona and the United States. I
uncovers how norms are created during periods of norm uncertainty and builds the
foundation to theorize and test interventions that promote positive norms in
times of disasters and uncertainty. Specifically, I investigate how local
diffusion leads to social norms through information search which will have
strong implications for the prevention of global polarization and the spread of
misinformation.

In academia and policy, the focus in research on information has always
been the information that is sent to consumers, seeing people as passive
receivers of information. My dissertation instead focuses on individuals as
active agents in their search for information. By looking at how individuals 
search, I aim to identify pain points and focus areas for future interventions
in the misinformation process.

The information that spread to communities in Arizona led to the health
behaviors exhibited today by Arizonans. While the information spread in various
ways, like through diffusion and polarization, it contributed to our newly
established norms in the Spring of 2020 and since. By uncovering how norms were
created during this time of norm uncertainty, my research will contribute to the
recommended interventions to promote effective health-related behavioral norms
before politicization and misinformation occurs. This will create a healthier,
happier Arizona.

@@

\subsection{Information Flow}
Humans have long been interested in how to persuade the masses. With the 
rise of democracy, the need of the powerful to persuade and appease the
masses dramatically increased. And for a while, behavioral scientists 
adopted really simplistic models of persuasion like the hypodermic needle model
\citep{bineham1988historical}. This simplistic perception of human behavior 
thought that the media basically injects messages into passive consumers
who wholly accept the message and are affected by its contents \citep{lasswellpropaganda}.

A critical turning point in the study of the flow of information was put forth by
renowned Sociologist Paul Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}.
Lazarsfeld and others theorized that the media did not directly influence the
masses, but that a "Two-Step Flow" was occurring where "opinion leaders"
interpreted messages from mass media and then, in turn, promoted their opinions
to the masses \citep{katzPersonalInfluencePart1955}. The opinion leaders
interpret, explain, and diffuse contents to "opinion followers". From a networks
perspective, "people rarely act on mass-media information unless it is also
transmitted through personal ties" \citep[p. 1374]{granovetterStrengthWeakTies1973}. 
Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}'s first study focused on
politics but follow up studies from \citep{katzPersonalInfluencePart1955} showed
that this model matched information flows beyond the political realm. In
contrast to the one-step flow, where media directly influences the masses,
Lazarsfeld's theory remains in prominence today. While many scholars assumed
that modern micro-targeted marketing strategies would provide evidence for a
one-step flow perspective \citep{bennettOneStepFlowCommunication2006}, many
scholars find that "opinion leaders" (often influencers and celebrities) still
create a two-step flow of information transmission \citep{choi15,
hilbertOneStepTwo2017}.

The spread of information has been thoroughly studied from the perspective
of social networks. Individuals engage with each other and their distributive
ties to create community contexts where norms, beliefs, and values circulate.
Information diffuses through communities and social networks
\citep{fowler2010cooperative, bond_etal12, klarEffectNetworkStructure2017}.
However, "different things spread in different ways and to different extents"
\citep[p. 563]{christakisSocialContagionTheory2013} and information can spread
differently than a virus or behavior. Important studies in the spread of
information through networks include the study of adoption of innovations by
physicians \citep{colemanDiffusionInnovationPhysicians1957}, how new inventions
are adopted from early adopters to laggards
\citep{rogersDiffusionInnovations1962}, how weak ties help bind networks and
diffuse information \citep{granovetterStrengthWeakTies1973}, how social ties
spread information about job opportunities
\citep{granovetterGettingJobStudy1995, montgomeryJobSearchNetwork1992}, how
information spreads best when weak and strong ties are balanced (embeddedness)
\citep{uzziSocialStructureCompetition1997}, and more recent innovations in the
stickiness of complex contagion \citep{centolaComplexContagionsWeakness2007}.

\subsection{Information Search}
I have only discussed the way that information is passively
consumed through push efforts by opinion leaders and social networks. However,
sociological literature is sparse on the opposite behavior: active
directed searching by individuals to obtain information.
\citep{pejtersenDesignComputeraidedUsersystem1984}, a scholar of library and
information science, theorized that there are 5 strategies for searching for
information. The most common strategy is browsing, where people follow leads
based on associations without planning. Another strategy is analytical,
which includes an explicit consideration of all facets of the question to guide
a search. The empirical method guides the search based on tactics that were
successful in past research. The known site strategy is to go to the direct
source of the information if known. And finally, the similarity method is to
find information based on another similar question that already has an answer.
These 5 strategies vary in their demands for prior knowledge, cognitive
processing, memory, and time spent. While this theory is aimed at finding
information in a library setting, scholars have extended the theory to other
fields and validated the framework \citep{fidelHumanInformationInteraction2012};
the frame is a useful beginning point for the theories of information search
through network activation or through computer-mediated communication.

@@

The introduction of the internet and digital technologies introduced an epochal
disruption in the communication and informational-search mediums that people had
available to them. Computer-mediated communication was the largest communication
revolution in a century, changing the speed and availability of communication
between individuals by electronic mail, instant messaging, two-way interactive
video calls, discussion forums, blogs, and social networking
\citep{rainie2012networked}. Computer-mediated communication encompasses any
sort of communication through computers connected to the internet; the umbrella
term involves both synchronous and asynchronous communication as well as
one-to-one, one-to-many, or many-to-many exchanges. Social media, on the other
hand, are more specific, and are "Internet-based, disentrained, and persistent
channels of mass personal communication facilitating perceptions of interactions
among users, deriving value primarily from user-generated content.” \citep[][p.
50]{carr2015social}. While an email between colleagues is computer-mediated
communication, it is not social media as there is only one interaction between
users and there is no value derived from the user-generated content outside the
pair \citep{bayer_etal20}. Even more restrictive still is the social networking
site, which consists of a profile, a network, and a stream or a feed
\citep{boyd2007social, ellison2013sociality},  often also involving a messaging
component  \citep{bayer_etal20}. Social networking sites are also interesting
because they often uniquely combine one-to-one communication within the context
of one-to-many communication, like resharing a television news story to your
Facebook feed and chatting with others about the content in the comments
section. But what do these classifications mean for the information-seeking
behaviors of individuals in the 21st century? Not only is it quicker to perform
network activation and seek support, but people are "permanently online,
permanently connected" making activation easy \citep{vorderer2017permanently}.
The constant connectedness facilitates communication, but also presents people
with overchoice, or the difficulty in deciding because simply every
network connection you may want to activate is permanently connected and easy to
reach. In other words, constant connection may be debilitating to many who are
seeking information. \citet{smallSomeoneTalk2017} provides many examples of this
when he demonstrates that often, graduate students who needed
support simply asked "miscellaneous classmates encountered down the hall" (p.
176) rather than their trusted, long-term confidants. It seems that network
activation may rely on more than just trust; namely: convenience.

The digital age did not only revolutionize communication. It also
revolutionized information search \citep{ramirez2002information}. Just as prior
to the digital age you could open an encyclopedia or peruse the library to find
the information you seek, much of the computer-mediated information search
surely occurs outside of social network activation contexts. While searching in
an encyclopedia is far less common today, internet search engines have
revolutionized the speed and ease at which we can find information. Early web
search engines allowed information seekers to browse web directories and early
engines like Yahoo! and Altavista found success using keyword-based search,
though the early algorithms were limited in what they could find and relied
heavily on the wording of the queries. Google, the major web search engine used
today, introduced the disruptive PageRank algorithm in the early 2000s, securing
its place as the information hegemon of the 21st century
\citep{brin1998anatomy}. Not only has computer-mediated information search
revolutionized the ease of obtaining information, but it has also changed our
brains. \citet{sparrow2011google} show that the digital age has led to worse
memory and higher reliance on technology to keep track of information for us.
These search engines have also shaped our cultures by controlling, whether
through algorithm or intentionally, the information the engine provides. For
example, Google will not show results for various neo-Nazi websites in countries
where holocaust denial is illegal, like France and Germany. This is illustrative
of the control engines have over information and how this control may introduce
various political, economic, and social biases in the information they provide
\citep{segev2010google}. When 99Firms \citeyearpar{99firms22} compiled the data
from sources like NetMarketShare, Statista, DuckDuckGo, Yahoo Finance, Google,
and Pew Research they found that about Around 93\% of all web traffic is
via a search engine and that 78.39\% of all internet searches performed are done
so using Google. Because computer-mediated information search is instantaneous 
and only requires mobile data or WiFi, there is virtually no cost to seeking
information on one of these mediums.

@@

One way to find information is to activate network ties to find out information
through a form of social support. Social support, while previously used
interchangeably with the term social networks and social integration
\citep{houseStructuresProcessesSocial1988}, are the emotional, informational,
and instrumental assistance functions performed between social ties and have
strong and measurable association with health outcomes
\citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}.
Informational support is the process of seeking "help in defining,
understanding, and coping with problematic events and include education, advice,
or referral to another source of support" \citep[p. 640]{winemiller_etal93}.
Brashers, a health communications researcher, defines informational support
slightly differently, focusing on the exchange of information that "facilitates
coping with life stresses... that may be exchanged among members of a support
network" \citeyearpar[p. 260]{brashersInformationSeekingAvoiding2002}. Both
definitions provide important lenses for my question of how
computer-mediated or interpersonal information-seeking strategies vary. 
Some research has revealed that Facebook users who utilize the platform to 
find information and to maintain relationships have high levels of bridging
social capital \citep{liu2016meta}. However, this leaves the question 
of who activates their social networks for information using social networking 
sites like Facebook instead of activating these networks in face-to-face
interactions.

@@

Adapting UGT to my own purposes, I theorize that
informational support will be activated from network ties when the informational
need is related to forming and deepening social ties
\citep{baumeister,grieve2013face} but search will be conducted outside of network
activation when information is needed but an individual does not have an additional cognitive
need to fill through social interaction. Alternative goals such as identity
management or relational maintenance
\citep{brashersInformationSeekingAvoiding2002} need to be balanced and may also
influence where search is conducted.

\subsection{Social Norms}
I showed that the levels of uncertainty may direct how and when people
search for information. However, in situations of rapidly changing norms,
uncertainty is prevalent. This dissertation will also focus on developing
new social norms in situations of uncertainty about how to behave. 
Minimal research exists in quickly emerging
norms in times of emergency but shows that people are likely to rely on the
behavior of others to set their own norms for behavior \citep{alvarez2018,
horneNormsIntegratedFramework2020}. This project will investigate how search
contributes to the development of said spontaneous norms.

@@

\citet{goldbergSocialContagionAssociative2018} argue that the state of the
literature on diffusion and social contagion, discussed above, is erroneous.
They propose an important linkage that had been missed in previous research of
the diffusion of behavior (or, as I interpret it, the creation of new norms).
They argue that what actually diffuses during social contagion are the
perceptions about which beliefs or behaviors are compatible with one another,
what they call "associative diffusion". 
This relates back to the theory of relational norms, where individuals assume
what their peers will approve and disapprove of. For these assumptions 
to take place, they must understand which behaviors and beliefs
are possessed by whom in their network and how new associations may influence
or disrupt the expected actions. In times of behavioral uncertainty, I
theorize that individuals strategically look towards other high-status
individuals, institutions, and perform regimented searches to establish for
themselves the behavior that is compatible with other cognitive associations
and biases they hold.

@@

To investigate information-seeking behaviors, online search tools, and how
new norms in health behaviors form, I first provide an outline of the 
information push and pull process in figure \ref{fig:concept-map}. After 
being exposed to new information, an actor can choose to further investigate
the information online or offline and, in turn, further share the 
information they were exposed to.

@@

This dissertation uses three articles to investigate different parts of
the theoretical framework (figure \ref{fig:concept-map}).
The dissertation is divided into three parts, with Article 1 focusing 
on online information search, Article 2 focusing on online and offline
information search, and Article 3 investigating the entire information
push and pull process in the context of establishing new norms.

@@

Computational social science and other disciplines are quick to adopt new
sources of digital trace data for use in academic research. In this article, I
examine the validity of one of these new sources, Google Search Trends. I
validate how Google Trends can be used to demonstrate three different cases,
namely attitudes, disease prevalence and political preferences using eight %TODO double check number
different validated data sources. This paper asks, "How can we operationalize
Google Search Trends as a valid indicator for uses in social science research?"
I use Pearson and Repeated Measures Correlations between the Google Trends and
the validated indicators as well as multiple linear regression (for
cross-sectional datasets) and random intercept hierarchical linear models (for
longitudinal datasets) as additional tests of the data.

I fail to find correlation among any of the Google Trends tested and their
validated indicators. While some Google Trends tested were significantly
associated with the outcome in the regression models, effects tended to be small
and the total model interpretability remained low, even when controlling for
demographic variables. This article shows that there is no external validity of
Google Trends for these uses and social scientists will find no replacement for
high quality survey data with Google Trends. Instead, we must only use 
Google Trends to demonstrate interest or attention.

@@

Knowing that Google trends data only encompasses a small portion of the
information-seeking done by modern humans, it is important to
investigate what leads individuals to search for a question online using
a search engine versus more
traditional means of information gathering, such as network activation
(asking someone in their social network for informational support). 
Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline. Using theories of social
support and uses and gratifications theory, I investigate the factors associated
with each information seeking vehicle: personal connection,
doctor, social networking site, online forum, and online search engine. I use
original survey data of 948 Americans to investigate their experiences seeking out
information about the COVID-19 vaccines.

This paper aims to address two main questions:
\begin{itemize}
  \item How do computer-mediated or interpersonal information-seeking strategies vary
across populations?
  \item How does the information search vehicle utilized affect COVID-19 Vaccination uptake? 
\end{itemize}

In this article, I find little evidence that online search is more utilized than
seeking social support from personal network connections or health professionals
as I hypothesize based on uses and gratifications theory. I find evidence that
the categorizations of vehicles queried in this survey are indeed conceptually
different from each other and that the utilization of different vehicles varies
by demography and information exposure points. Finally, I find that different
exposure points and information search vehicles hold real world consequences
through their associations with COVID-19 vaccination rates and intentions, as
information from a doctor increases the COVID-19 vaccination uptake while
receiving information from a Social Networking Site like Facebook or Twitter was
associated with lower odds of vaccination.

@@

My final article takes a deeper dive into the formation of social norms
governing health behaviors in cases of extreme uncertainty using the cases of
both stay-at-home rates and vaccination rates as responses to public health recommendations to mitigate the COVID-19 pandemic. Using theories of associative diffusion and the integrated
theoretical framework of norms, I test models of behavioral adaption to public health
recommendations as well as patterns of complex social contagion using linear
mixed effects models.

These models show that complex contagion is a valid 
framework for the social contagion of new norms during COVID-19. Importantly, I find
a novel moderating effect of signal discordance, the contextual diversity of
signals received by an ego. This paper shows that the contagion process is not
fully understood without looking at the context of each exposure point within the
range of exposures one experiences.

@@

% search as an agentic process
This research will make contributions to multiple subfields and literatures. 
First and foremost, these articles contribute to the sociological literature.
The spread of information has long been investigated in the discipline (diffusion, mass
communication, social influence). However, it is almost always researched from a structural
perspective which disregards individual agency and choice in the
acquisition of new information. This dissertation adopts the second perspective,
centering people as active agents in their search for information aligned
with their own preferences and gratifications instead of just
passive receivers of information signals.
Taking this agentic perspective is critical in the study of information
diffusion when combined with cognitive perspectives like that of
Goldberg and Stein (2018). How people search for information determines
the information that they find. The information they uncover is filtered
through cognitive biases and predispositions to how they interpret and
act upon the newfound information. Searching for informational support
through social network ties theoretically will uncover potentially
different information than that would be uncovered through online web
search and will change how people are organized and how people behave.
\hyperlink{paper-2}{Article 2} importantly shows that 
the vehicles used to search for information have a significant impact on the choice to get vaccinated against COVID-19, a real-world consequence to the minutiae of individual information search.

@@

% micro behaviors to macro processes
Bridging the contribution of search as an agentic process 
and critical big data studies, this dissertation contributes to the question posed by 
\citet{breigerScaling2015}, "what are the behavioral processes that 
lead to macro-level outcomes?" With the exponentially growing size of digital-trace data
that is available, it is important to not only uncover the external validity of 
the data and correspondence to real world behaviors (see \hyperlink{paper-1}{Article 1})
but also important to understand the social forces that leads to the big data. 
One of the contributions of \hyperlink{paper-2}{Article 2} dives deep
into this question, uncovering why some people choose to use web search engines over other
information-vehicles. These papers are a first step in validating and establishing
a deeper understanding of who the users are that contribute to macro-level aggregate trends.

>>>>

\hypertarget{intro}
{\chapter{Introduction}\label{intro}}

This dissertation focuses on how people search for information and how people
rely on this information to inform their health behaviors and develop social
norms. Information permeates every facet of human society, from the hordes of
data gathered through digital-trace data or the passing gossip between friends.
Human communication and human society are based on the circulation of
information and knowledge. Information can be shared and promoted by others
through information campaigns and consumed by an individual, called information
push, or information can be intentionally sought out by individuals, 
called information pull \citep{cybenkoFoundationsInformationPush1999}.

@@

The importance of reputable information and misinformation was clear
in the recent and ongoing COVID-19 pandemic. While the vaccines against the
COVID-19 virus are effective in preventing severe illness, hospitalization, 
and death, only 60\% of Arizonans over 12 years old \citep{owid}
are fully vaccinated against the virus. We know that
people exposed to misinformation are much less likely to receive vaccinations
against the virus \citep{loombaMeasuringImpactCOVID192021}. It is not an
exaggeration to claim that misinformation has been deadly for Arizona
\citep{pathakInfodemicsCOVID19Role2020, greene_murphy21}.

This dissertation on information search and norm development provides clear and
timely social implications for Arizona and the United States. I
uncover how norms are created during periods of norm uncertainty and builds the
foundation to theorize and test interventions that promote positive norms in
times of disasters and uncertainty. Specifically, I investigate how local
diffusion leads to social norms through information search, which will have
strong implications for the prevention of global polarization and the spread of
misinformation, as I now explain.

In academia and policy, the focus in research on information has always
been the information that is sent to consumers, seeing people as passive
receivers of information. My dissertation instead focuses on individuals as
active agents in their search for information. By looking at how individuals 
search, I aim to identify focus areas for future interventions
to counter the misinformation process.

The information that spread to communities in Arizona contributed to the health
behaviors exhibited today by Arizonans. While the information spread in various
ways, including by means of diffusion and polarization, it contributed to our newly
established norms in the Spring of 2020 and since. By uncovering how norms were
created during this time of norm uncertainty, my research will contribute to the
recommended interventions to promote effective health-related behavioral norms
before politicization and misinformation occurs. This will create a healthier,
happier Arizona.

@@

\subsection{Information Flow}
Humans have long been interested in how to persuade the masses. With the 
rise of democracy, the need of the powerful to persuade and appease the
masses dramatically increased. And for a while, behavioral scientists 
adopted really simplistic models of persuasion like the assumption
that the media influences behavior in a direct, unmediated, and 
all-powerful way (termed the hypodermic needle model in
\citet{bineham1988historical}) \citep{lasswellpropaganda}.

A critical turning point in the study of the flow of information was put forth by
renowned sociologist Paul Lazarsfeld and colleagues Verelson and Gaudet \citeyearpar{lazarsfeldPeopleChoice1944}.
They theorized that the media did not directly influence the
masses, but that a "Two-Step Flow" was occurring where "opinion leaders"
interpreted messages from mass media and then, in turn, promoted their opinions
to the masses \citep{katzPersonalInfluencePart1955}. The opinion leaders
interpret, explain, and diffuse contents to "opinion followers". From a networks
perspective, "people rarely act on mass-media information unless it is also
transmitted through personal ties" \citep[p. 1374]{granovetterStrengthWeakTies1973}. 
Lazarsfeld et al's \citeyearpar{lazarsfeldPeopleChoice1944} first study focused on
politics, but follow up studies by \citet{katzPersonalInfluencePart1955} showed
that this model matched information flows beyond the political realm. In
contrast to the one-step flow, where media directly influences the masses,
Lazarsfeld's theory remains in prominence today. While many scholars assumed
that modern micro-targeted marketing strategies would provide evidence for a
one-step flow perspective \citep{bennettOneStepFlowCommunication2006}, many
scholars find that "opinion leaders" (often influencers and celebrities) still
create a two-step flow of information transmission \citep{choi15,
hilbertOneStepTwo2017}.

The spread of information has been thoroughly studied from the perspective
of social networks. Individuals engage with each other and their distributed
ties to create community contexts where norms, beliefs, and values circulate.
Information diffuses through communities and social networks
\citep{fowler2010cooperative, bond_etal12, klarEffectNetworkStructure2017}.
However, "different things spread in different ways and to different extents"
\citep[p. 563]{christakisSocialContagionTheory2013} and information can spread
differently than a virus or behavior. Important studies in the spread of
information through networks include the study of adoption of innovations by
physicians \citep{colemanDiffusionInnovationPhysicians1957}, how new inventions
are adopted from early adopters to laggards
\citep{rogersDiffusionInnovations1962}, how weak ties help bind networks and
diffuse information \citep{granovetterStrengthWeakTies1973}, how social ties
spread information about job opportunities
\citep{granovetterGettingJobStudy1995, montgomeryJobSearchNetwork1992}, how
information spreads best when weak and strong ties are balanced (embeddedness)
\citep{uzziSocialStructureCompetition1997}, and more recent innovations in the
stickiness of complex contagion \citep{centolaComplexContagionsWeakness2007}.

\subsection{Information Search}
I have only discussed the way that information is passively
consumed through push efforts by opinion leaders and social networks. However,
sociological literature is sparse on the opposite behavior: active
directed searching by individuals to obtain information.
\citet{pejtersenDesignComputeraidedUsersystem1984}, a scholar of library and
information science, theorized that there are 5 strategies for searching for
information. The most common strategy is browsing, where people follow leads
based on associations without planning. Another strategy is analytical,
which includes an explicit consideration of all facets of the question to guide
a search. The empirical method guides the search based on tactics that were
successful in past research. The known site strategy is to go to the direct
source of the information if known. And finally, the similarity method is to
find information based on another similar question that already has an answer.
These 5 strategies vary in their demands for prior knowledge, cognitive
processing, memory, and time spent. While this theory is aimed at finding
information in a library setting, scholars have extended the theory to other
fields and validated the framework \citep{fidelHumanInformationInteraction2012};
the frame is a useful beginning point for the theories of information search
through network activation or through computer-mediated communication.

@@

The introduction of the internet and digital technologies introduced an epochal
disruption in the communication and informational-search mediums that people had
available to them. Computer-mediated communication was the largest communication
revolution in a century, changing the speed and availability of communication
between individuals by electronic mail, instant messaging, two-way interactive
video calls, discussion forums, blogs, and social networking
\citep{rainie2012networked}. Computer-mediated communication encompasses any
sort of communication through computers connected to the internet; the umbrella
term involves both synchronous and asynchronous communication as well as
one-to-one, one-to-many, or many-to-many exchanges. Social media, on the other
hand, are more specific, and are "Internet-based, disentrained, and persistent
channels of mass personal communication facilitating perceptions of interactions
among users, deriving value primarily from user-generated content” \citep[][p.
50]{carr2015social}. While an email between colleagues is computer-mediated
communication, it is not social media as there is only one interaction between
users and there is no value derived from the user-generated content outside the
pair \citep{bayer_etal20}. Even more restrictive still is the social networking
site, which consists of a profile, a network, and a stream or a feed
\citep{boyd2007social, ellison2013sociality},  often also involving a messaging
component  \citep{bayer_etal20}. Social networking sites are also interesting
because they often uniquely combine one-to-one communication within the context
of one-to-many communication, like resharing a television news story to your
Facebook feed and chatting with others about the content in the comments
section. But what do these classifications mean for the information-seeking
behaviors of individuals in the 21st century? Not only is it quicker to perform
network activation and seek support, but people are "permanently online,
permanently connected" making activation easy \citep{vorderer2017permanently}.
The constant connectedness facilitates communication, but also presents people
with overchoice, or the difficulty in deciding because simply every
network connection you may want to activate is permanently connected and easy to
reach. In other words, constant connection may be debilitating to many who are
seeking information. \citet{smallSomeoneTalk2017} provides many examples of this
when he demonstrates that often, graduate students who needed
support simply asked "miscellaneous classmates encountered down the hall" (p.
176) rather than their trusted, long-term confidants. It seems that network
activation may rely on more than just trust; namely: convenience.

The digital age did not only revolutionize communication. It also
revolutionized information search \citep{ramirez2002information}. Just as prior
to the digital age you could open an encyclopedia or peruse the library to find
the information you seek, much of the computer-mediated information search
surely occurs outside of social network activation contexts. While searching in
an encyclopedia is far less common today, internet search engines have
revolutionized the speed and ease at which we can find information. Early web
search engines allowed information seekers to browse web directories, and early
engines like Yahoo! and Altavista found success using keyword-based search,
though the early algorithms were limited in what they could find and relied
heavily on the wording of the queries. Google, the major web search engine used
today, introduced the disruptive PageRank algorithm in the early 2000s, securing
its place as the information hegemon of the 21st century
\citep{brin1998anatomy}. Not only has computer-mediated information search
revolutionized the ease of obtaining information, but it has also changed our
brains. \citet{sparrow2011google} show that the digital age has led to worse
memory and higher reliance on technology to keep track of information for us.
These search engines have also shaped our cultures by controlling, whether
through algorithm or intentionally, the information the engine provides. For
example, Google will not show results for various neo-Nazi websites in countries
where holocaust denial is illegal, like France and Germany. This is illustrative
of the control engines have over information and how this control may introduce
various political, economic, and social biases in the information they provide
\citep{segev2010google}. When 99Firms \citeyearpar{99firms22} compiled the data
from sources like NetMarketShare, Statista, DuckDuckGo, Yahoo Finance, Google,
and Pew Research they found that about 93\% of all web traffic is
via a search engine and that 78.39\% of all internet searches performed are done
using Google. Because computer-mediated information search is instantaneous 
and only requires mobile data or WiFi, there is virtually no cost to seeking
information on one of these mediums.

@@

One way to find information is to activate network ties to find out information
through a form of social support. Social support, while previously used
interchangeably with the term social networks and social integration
\citep{houseStructuresProcessesSocial1988}, consisted of the emotional, informational,
and instrumental assistance functions performed by social ties. Social 
support has strong and measurable association with health outcomes
\citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}.
Informational support is the process of seeking "help in defining,
understanding, and coping with problematic events and include education, advice,
or referral to another source of support" \citep[p. 640]{winemiller_etal93}.
Brashers, a health communications researcher, defines informational support
slightly differently, focusing on the exchange of information that "facilitates
coping with life stresses... that may be exchanged among members of a support
network" \citeyearpar[p. 260]{brashersInformationSeekingAvoiding2002}. Both
definitions provide important lenses for my question of how
computer-mediated or interpersonal information-seeking strategies vary. 
Some research has revealed that Facebook users who utilize the platform to 
find information and to maintain relationships have high levels of bridging
social capital \citep{liu2016meta}. However, this leaves the question 
of who activates their social networks for information using social networking 
sites like Facebook instead of activating these networks in face-to-face
interactions.

@@

Adapting UGT to my own purposes, I theorize that
informational support will be activated from network ties when the informational
need is accompanied by or related to a need to form or maintain social ties
\citep{baumeister,grieve2013face}. For instance, Dani, a young college student, 
could search on Google to find how to turn iron their dress shirt properly, 
but instead Dani choses to call their parent(s) and ask the best strategy so their parent(s)
feels respected and valued and their relationship is strengthened. 
Conversely, I theorize that search will be conducted outside of network
activation when information is needed but an individual does not have 
an additional cognitive need to fill through social interaction. 
For example, Taylor could ask their neighbor who is a medical professional about 
the newfound headaches they've been experiencing, but every time they talk to their
neighbor they ask for help cleaning their gutters, which is too much work; Taylor
instead may choose to ask the Facebook group they're a part of to gain information.
Alternative goals such as identity management or relational maintenance
\citep{brashersInformationSeekingAvoiding2002} need to be balanced and may also
influence where search is conducted.

\subsection{Social Norms}
I showed that the levels of uncertainty may direct how and when people
search for information. However, in situations of rapidly changing norms,
uncertainty is prevalent. This dissertation also focuses on the development of
new social norms in situations of uncertainty about how to behave. 
Minimal research exists in quickly emerging
norms in times of emergency but shows that people are likely to rely on the
behavior of others to set their own norms for behavior \citep{alvarez2018,
horneNormsIntegratedFramework2020}. This project investigates how search
contributes to the development of said spontaneous norms.

@@

\citet{goldbergSocialContagionAssociative2018} argue that the state of the
literature on diffusion and social contagion, discussed above, is erroneous.
They propose an important linkage that had been missed in previous research of
the diffusion of behavior (or, as I interpret it, the creation of new norms).
They argue that what actually diffuses during social contagion are the
perceptions about which beliefs or behaviors are compatible with one another,
what they call "associative diffusion". 
This relates back to the theory of relational norms, where individuals assume
what their peers will approve and disapprove of. For these assumptions 
to take place, they must understand which behaviors and beliefs
are possessed by whom in their network and how new associations may influence
or disrupt the expected actions. In times of behavioral uncertainty, I
theorize that individuals strategically look towards other high-status
individuals and institutions, and perform regimented searches to establish for
themselves the behavior that is compatible with other cognitive associations
and biases they hold.

@@

To investigate information-seeking behaviors, online search tools, and how
new norms in health behaviors form, I first provide an outline of the 
information push and pull process in Figure \ref{fig:concept-map}. After 
being exposed to new information, an actor can choose to further investigate
the information online or offline and, in turn, further share the 
information they were exposed to.

@@

This dissertation uses three articles to investigate different parts of
the theoretical framework (Figure \ref{fig:concept-map}).
The dissertation is divided into three parts, with Article 1 focusing 
on online information search, Article 2 focusing on online and offline
information search, and Article 3 investigating the entire information
push and pull process in the context of establishing new norms.

@@

Computational social science and social science disciplines are quick to adopt new
sources of digital trace data for use in academic research. In this article, I
examine the criterion validity of one of these new sources, Google Search Trends. I
validate how Google Trends can be used to demonstrate three different cases,
namely attitudes, disease prevalence and political preferences using five
different validated data sources. This paper asks, "How can we operationalize
Google Search Trends as a valid indicator for uses in social science research?"
I use Pearson and Repeated Measures Correlations between the Google Trends and
the validated indicators as well as multiple linear regression (for
cross-sectional datasets) and random intercept hierarchical linear models (for
longitudinal datasets) as additional tests of the data.

I fail to find correlation among any of the Google Trends tested and their
validated indicators. While some Google Trends tested were significantly
associated with the outcome in the regression models, effects tended to be small
and the total model interpretability remained low, even when controlling for
demographic variables. This article shows that there is no external or 
criterion validity of Google Trends for these uses and social scientists will find no replacement for
high quality survey data with Google Trends. Instead, we must only use 
Google Trends to demonstrate interest or attention.

@@

Knowing that Google trends data only encompasses a small portion of the
information-seeking done by modern humans, it is important to
investigate what leads individuals to search for a question online using
a search engine versus more
traditional means of information gathering, such as network activation
(asking someone in their social network for informational support). 
Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline. Using theories of social
support and uses and gratifications theory, I investigate the factors associated
with each information seeking modality: personal connection,
doctor, social networking site, online forum, and online search engine. I use
original survey data of 948 Americans to investigate their experiences seeking out
information about the COVID-19 vaccines.

This paper aims to address two main questions:
\begin{itemize}
  \item How do computer-mediated or interpersonal information-seeking strategies vary
across populations?
  \item How does the information search modality utilized affect COVID-19 Vaccination uptake? 
\end{itemize}

In this article, I find little evidence that online search is more utilized than
seeking social support from personal network connections or health professionals
as I hypothesize based on uses and gratifications theory. I find evidence that
the categorizations of modalities queried in this survey are indeed conceptually
different from each other and that the utilization of different modalities varies
by demography and information exposure points. Finally, I find that different
exposure points and information search modalities hold real world consequences
through their associations with COVID-19 vaccination rates and intentions, as
information from a doctor increases the COVID-19 vaccination uptake while
receiving information from a social networking site like Facebook or Twitter was
associated with lower odds of vaccination.

@@

My final article takes a deeper dive into the formation of social norms
governing health behaviors in cases of extreme uncertainty using the cases of
both stay-at-home rates and vaccination rates as responses to public health recommendations to mitigate the COVID-19 pandemic. Using theories like associative diffusion
and the integrated theoretical framework of norms, I test models of behavioral adaption
to public health recommendations and patterns of complex contagion (the need for
repeated exposures to a something novel for it to diffuse) using linear
mixed effects models.

These models show that complex contagion is a valid 
framework for the social contagion of new norms during COVID-19. Importantly, I find
a novel moderating effect of signal discordance, the contextual diversity of
signals received by an ego. If there is diversity in the information received
by an ego, contagion is less likely to occur. This paper shows that the contagion 
process cannot be not fully understood without looking at the context of each
exposure to a contagion within  within the range of contagions one experiences.

@@

% search as an agentic process
This research makes contributions to multiple subfields and literatures. 
First and foremost, these articles contribute to the sociological literature.
The spread of information has long been investigated in the discipline (diffusion, mass
communication, social influence). However, it is almost always researched from a structural
perspective which disregards individual agency and choice in the
acquisition of new information. This dissertation adopts the second perspective,
centering people as active agents in their search for information aligned
with their own preferences and gratifications instead of just
passive receivers of information signals.
Taking this agentic perspective is critical in the study of information
diffusion when combined with cognitive perspectives like that of
\citet{goldbergSocialContagionAssociative2018}. How people
search for information is a strong determinant of 
the information that they find. The information they uncover is filtered
through cognitive biases and predispositions to how they interpret and
act upon the newfound information. Searching for informational support
through social network ties theoretically will uncover potentially
different information than would be uncovered through online web
search and will change how people are organized and how people behave.
\hyperlink{paper-2}{Article 2} Article 2, for instance, demonstrates that 
the choice to receive a COVID-19 vaccine is impacted by how
individuals search for information on the vaccine. 
This is a real-world consequence to the variation in the individual information
search process.

@@

% micro behaviors to macro processes
Bridging the contribution of search as an agentic process 
and critical big data studies, this dissertation contributes to the question posed by 
\citet{breigerScaling2015}, "what are the behavioral processes that 
lead to macro-level outcomes?" With the exponentially growing size of digital-trace data
that is available, it is important to not only uncover the external and criterion validity of 
the data and correspondence to real world behaviors (see \hyperlink{paper-1}{Article 1})
but also important to understand the social forces that lead to the big data. 
One of the contributions of \hyperlink{paper-2}{Article 2} is to dive deep
into this question, uncovering why some people choose to use web search engines over other
information search modalities. These papers are a first step in validating and establishing
a deeper understanding of who the users are that contribute to macro-level aggregate trends.
